iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-30 manuscript/main.tex

\section*{Author contributions}
All authors contributed conceptually and technically to the development and maintenance of large sections of the package code.
A.T.L.L. and F.M. developed the application and data infrastructure.
K.R.A and C.S. developed the plotting framework.
F.M. developed the code tracking and user interface.
K.R.A designed and developed the ExperimentColorMap class.
All authors contributed to testing the application on all data sets.
All authors wrote and approved the final manuscript.

>>>>

\section*{Author contributions}
All authors contributed conceptually and technically to the development and maintenance of large sections of the package code.
ATLL and FM developed the application and data infrastructure.
KRA and CS developed the plotting framework.
FM developed the code tracking and user interface.
KRA designed and developed the ExperimentColorMap class.
All authors contributed to testing the application on all data sets.
All authors wrote and approved the final manuscript.
